|

### 2020-05-08 paper/Manuscript.Rmd
Marijn changes

The second solution is *version control*: Maintaining an indelible log of every change to all project files. Version control is a near-essential tool for scientific reproducibility, as anyone learns who has had the experience of accidentally deleting a crucial file, or of being unable to reproduce analyses because they ran some analyses interactively instead of using syntax [see also @blischakQuickIntroductionVersion2016]. Many scientists use some form of *implicit* version control; for example, by renaming files after major changes (e.g., "manuscript_final_2.2-2019-10-12.doc"), tracking changes in word processing software, or using cloud hosting services that retain backups of previous versions. WORCS instead uses the *explicit* version control software "Git". Git tracks changes to files, and stores these changes when the user makes a "commit". Git retains a complete log of all commits, and users can compare changes between different commits, or go back to a previous version of the code (for example, after making a mistake, or to replicate a previous version of the results). A project version controlled with Git is called a "Repository", or Repo.

@@

One important impediment to comprehensive citation is the fact that print journals operate with space constraints. Print journals often discourage comprehensive citation, either actively, or passively by including the reference list in the manuscript word count. Researchers can overcome this impediment by preparing two versions of the manuscript: One version with comprehensive citations for online dissemination, and another version for print, with only the essential citations. The print version should reference the online version in the print version, so interested readers can find the comprehensive reference list. Step 20 of the WORCS procedure suggests uploading the online version to a preprint server. This is important because most preprint servers - [at least the ones hosted by OSF.io](https://help.osf.io/hc/en-us/articles/360019930493-Preprint-FAQs#how_do_i_find_preprints) - are indexed by Google Scholar. This means that authors will receive credit for cited work; even if they are cited only in the online version. Moreover, preprint servers ensure that the online version will have a persistent DOI, and will remain reliably accessible, just like the print version.

It is easiest to mark the distinction between essential and non-essential references from the start, instead of going back to cut references prior to publication. Therefore, the `worcs` package distinguishes between the traditional at-symbol (`@`) used to cite a reference, and the "double at"-symbol (`@`), used to cite a non-essential reference. Users can render a manuscript to PDF either with, or without, comprehensive citations.

@@

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).

@@

Data sharing is important for computational reproducibility and secondary analysis. Computational reproducibility means that a third party can exactly recreate the results from the raw data, using the published analysis code. Secondary analysis means that a third party can conduct sensitivity analyses, explore alternative explanations, or even use existing data to answer a different research question. From an open science perspective, data sharing is always desirable. From a practical point of view, it is not always possible. Data sharing may be impeded by legal constraints, ethical restrictions, absence of informed consent for data sharing, and privacy concerns. In some cases, it is difficult or impossible to share data.

@@

When data cannot be shared, researchers should aim to safeguard the potential for computational reproducibility and secondary analysis as much as possible. WORCS uses two solutions to accomplish this goal. The first solution is publishing a *checksum* of the raw data upon collection. A checksum is a 32-character summary of a file of any size. Any change to the underlying file results in a different checksum. Thus, one can use a checksum to verify that the contents of a file remain unchanged. If researchers publish the checksum of their raw data and the complete analysis code, then they can prove to an independent auditer that running the public analysis code on the private dataset with the correct checksum results in the published results of their work.

@@

* `open_data(data)`: This function takes a data object (a `data.frame` or `matrix`), writes it to a file called `data.csv`, updates the `.gitignore` file to stop ignoring this specific `.csv` file, and writes a checksum for this data file to `checksums.csv`. The data can now be committed and pushed to GitHub, where they will be open once the GitHub repository is made public.
* `closed_data(data)`: This function generates a local file called `data.csv`, and a synthetic dataset called `synthetic_data.csv`, updates the `.gitignore` file to stop ignoring `synthetic_data.csv` file, and writes a checksum for the real data file to `checksums.csv`. The synthetic data can now be committed and pushed to GitHub, and the real data will be ignored by Git.

Typically, the last line of the `prepare_data.R` file will thus be `open_data()` or `closed_data()`. The code for analysis of the data, on the other hand, will typically begin with `load_data()`. This function loads the real data if it is available (i.e., the file `data.csv` exists, and its checksum is correct), and otherwise, loads the synthetic data. This will have the effect that third party users who copy the GitHub repository will automatically load the synthetic dataset, whereas the study authors, who have the real data stored locally, will automatically load the real data.

@@

1. Create a new Private repository on GitHub, and copy the repository link to the clipboard. The link will look like https://github.com/yourname/yourrepo.git
2. In RStudio, click File > New Project > New directory > WORCS Project Template
    a. Paste the GitHub Repository address in the textbox
    b. Keep the checkbox for `renv` checked if you want to document all dependencies (recommended). The only reason not to do this is if you have dependencies outside of the R environment, or if you are using a more comprehensive solution for computational reproducibility, e.g., @peikertReproducibleDataAnalysis2019.
    c. Select a preregistration template
    d. Click Open in new session, and Create project
3. Write the preregistration `preregistration.Rmd`
4. In the top-right corner of RStudio, select the Git tab, select the checkboxes next to all files, and click the Commit button. Write an informative message for the commit, e.g., "Preregistration", again click Commit, and then click the green Push arrow to send your commit to GitHub
5. Go to the GitHub repository for this project, and tag the Commit as a preregistration
6. Optional: Render the preregistration to PDF, and upload it to AsPredicted.org or OSF.io as an attachment
7. Optional: Add study Materials (to which you own the rights) to the repository. It is possible to solicit feedback (by opening a GitHub Issue) and acknowledge outside contributions (by accepting Pull requests)

@@

8. Read the data into R, and document this procedure in `prepare_data.R`
9. Use `open_data()` or `closed_data()` to store the data
10. Write the manuscript in `Manuscript.Rmd`, using code chunks to perform the analyses.
11. Regularly commit your progress to the Git repository; ideally, after completing each small and clearly defined task. Use informative commit messages. Push the commits to GitHub.
12. Cite essential references with one at-symbol (`[@essentialref2020]`), and non-essential references with a double at-symbol (`[@nonessential2020]`).

>>>>

The second solution is *version control*: Maintaining an indelible log of every change to all project files. Version control is a near-essential tool for scientific reproducibility, as anyone learns who has had the experience of accidentally deleting a crucial file, or of being unable to reproduce analyses because they ran some analyses interactively instead of using syntax [see also @blischakQuickIntroductionVersion2016]. Many scientists use some form of *implicit* version control; for example, by renaming files after major changes (e.g., "manuscript_final_2.2-2019-10-12.doc"), tracking changes in word processing software, or using cloud hosting services that retain backups of previous versions. WORCS instead uses the *explicit* version control software "Git". Git tracks changes to files, and stores these changes when the user makes a "commit". Git retains a complete log of all commits, and users can compare changes between different commits, or go back to a previous version of the code (for example, after making a mistake, or to replicate a previous version of the results). A project version controlled with Git is called a "Repository", or Repo. It is also possible to prevent some files from being version controlled - such as privacy sensitive data. The `.gitignore` file is a list of files that should not be version-controlled, and thus exist only on the user's private computer.

@@

One important impediment to comprehensive citation is the fact that print journals operate with space constraints. Print journals often discourage comprehensive citation, either actively, or passively by including the reference list in the manuscript word count. Researchers can overcome this impediment by preparing two versions of the manuscript: One version with comprehensive citations for online dissemination, and another version for print, with only the essential citations. The print version should reference the online version, so interested readers can find the comprehensive reference list. Step 20 of the WORCS procedure suggests uploading the online version to a preprint server. This is important because most preprint servers - [at least the ones hosted by OSF.io](https://help.osf.io/hc/en-us/articles/360019930493-Preprint-FAQs#how_do_i_find_preprints) - are indexed by Google Scholar. This means that authors will receive credit for cited work; even if they are cited only in the online version. Moreover, preprint servers ensure that the online version will have a persistent DOI, and will remain reliably accessible, just like the print version.

It is easiest to mark the distinction between essential and non-essential references from the start, instead of going back to cut references prior to publication. Therefore, the `worcs` package distinguishes between the traditional at-symbol (`@`) used to cite a reference, and the "double at"-symbol (`@@`), used to cite a non-essential reference. Users can render a manuscript to PDF either with, or without, comprehensive citations.

@@

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).

@@

Data sharing is important for computational reproducibility and secondary analysis. Computational reproducibility means that a third party can exactly recreate the results from the raw data, using the published analysis code. Secondary analysis means that a third party can conduct sensitivity analyses, explore alternative explanations, or even use existing data to answer a different research question. From an open science perspective, data sharing is always desirable. From a practical point of view, it is not always possible. Data sharing may be impeded by legal constraints, ethical restrictions, absence of informed consent for data sharing, and privacy concerns. For example, the GDPR prohibits storing 'personal data' (information which can identify a natural person whether directly or indirectly) on a server outside the EU. Different rules may apply to anonymized or pseudonimized data. Before sharing any data, it is recommended to obtain approval from an internal (ethical) review board, guidance from Research Data Management Support, and informed consent from participants.

@@

When data cannot be shared, researchers should aim to safeguard the potential for computational reproducibility and secondary analysis as much as possible. WORCS uses two solutions to accomplish this goal. The first solution is publishing a *checksum* of the raw data upon collection. A checksum represents the contents of a file in a 32-character summary. Any change to the underlying file results in a different checksum. Thus, one can use a checksum to verify that the contents of a file remain unchanged. If researchers publish the checksum of their raw data and the complete analysis code, then they can prove to an independent auditer that running the public analysis code on the private dataset with the correct checksum results in the published results of their work.

@@

* `open_data(data)`: This function stores the data object (a `data.frame` or `matrix`) in a spreadsheet file called `data.csv`, stores a checksum for the file, and creates a codebook. All of these files should now be (manually) added to the 'Git' repository, committed, and pushed to GitHub. Once the GitHub repository is made public, these data will be open to the public.
* `closed_data(data)`: This function stores the data in a local file called `data.csv`, which is added to the `.gitignore` file so it cannot be accidentally added to the 'Git' repository. The function also creates a synthetic dataset called `synthetic_data.csv`. The user should commit all changed files and push them to GitHub. Once the GitHub repository is made public, people will have access to a checksum for the raw data that exist on your local machine, a codebook describing those data, and a synthetic copy of the data.

Some users may intend to share their data through a platform with restricted access (like an institutional repository), but not publically through GitHub. In this case, it is recommended to use `closed_data()`, and to manually upload the original data `data.csv` to the restricted access platform. If users wish to share their data through the Open Science Framework, it is sufficient to connect the OSF page to the GitHub repository.

The `prepare_data.R` file describes the data wrangling process to derive a spreadsheet ready for analysis. The final line of this file will often be `open_data()` or `closed_data()`. The code for analysis of the data, on the other hand, will typically begin with `load_data()`. This function loads the real data if it is available (i.e., the file `data.csv` exists, and the checksum is correct), and otherwise, loads the synthetic data. This will have the effect that third party users who copy the GitHub repository will automatically load the synthetic dataset, whereas the study authors, who have the real data stored locally, will automatically load the real data.

@@

1. Create a new Private repository on GitHub. Do not change any of the default options. Copy the repository link to the clipboard. This link will look like https://github.com/yourname/yourrepo.git
2. In RStudio, click File > New Project > New directory > WORCS Project Template
    a. Paste the GitHub Repository address in the textbox
    b. Keep the checkbox for `renv` checked if you want to document all dependencies (recommended). The only reason not to do this is if you have dependencies outside of the R environment, or if you are using a more comprehensive solution for computational reproducibility, e.g., @peikertReproducibleDataAnalysis2019.
    c. Select a preregistration template
    d. Click Open in new session, and Create project
3. Write the preregistration `preregistration.Rmd`
4. In the top-right corner of RStudio, select the Git tab, select the checkboxes next to all files, and click the Commit button. Write an informative message for the commit, e.g., "Preregistration", again click Commit, and then click the green Push arrow to send your commit to GitHub
5. Go to the GitHub repository for this project, and tag the Commit as a preregistration
6. Optional: Render the preregistration to PDF, and upload it to AsPredicted.org or OSF.io as an attachment
7. Optional: Add study Materials (to which you own the rights) to the repository. It is possible to solicit feedback (by opening a GitHub Issue) and acknowledge outside contributions (by accepting Pull requests)

@@

8. Read the data into R, and document this procedure in `prepare_data.R`
9. Use `open_data()` or `closed_data()` to store the data
10. Write the manuscript in `Manuscript.Rmd`, using code chunks to perform the analyses.
11. Regularly commit your progress to the Git repository; ideally, after completing each small and clearly defined task. Use informative commit messages. Push the commits to GitHub.
12. Cite essential references with one at-symbol (`[@essentialref2020]`), and non-essential references with a double at-symbol (`[@@nonessential2020]`).
